Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}

### 2025-07-09 rapport.tex
ajout petit paragraphe bilinearité

>>>>

		In our setting, we consider bilinear systems that are slightly overdetermined. We argue that when using hybrid methods such as \emph{Crossbred}, which avoid the need to construct Macaulay matrices up to high degrees—as required by algorithms like F5—the only reductions to zero that are likely to occur are those explained by the F5 and Frobenius criteria. Indeed, other types of reductions to zero typically appear at degrees $n_x + 1$ and $n_y + 1$ for bilinear systems, which are not reached in our practical use cases. Consequently, we consider these systems to behave in a semi-regular manner, although we believe they are, in practice, easier to solve.
